---
title: "Chapter B2 - Classes"
output: 
  html_document:
    highlight: null
    mathjax: null
    css: SFRPG.css

---



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
basedir <- dirname(getwd())
source(file.path(basedir,"scripts","1-01-Class-csv-to-html.R"))
classList <- getClassList(basedir)


```



## Universal Powers
The following powers are available to Player Characters of all classes.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Universal$Universal
cat(currentClass$powers.htm)
```


##Barbarian{.newPage}
###Build: Barbarian Rager

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Barbarian$Rager
cat(currentClass$stats.htm)
```
####Class Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$features.htm)
```
<br/>

####Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$powers.htm)
```


##Fighter{.newPage}
###Build: Fighter Guardian

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Fighter$Guardian
cat(currentClass$stats.htm)
```
####Class Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$features.htm)
```
<br/>

####Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$powers.htm)
```


##Priest{.newPage}
###Build: Priest of Light

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Priest$Light
cat(currentClass$stats.htm)
```
####Class Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$features.htm)
```
<br/>

####Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$powers.htm)
```


##Rogue{.newPage}
###Build: Scoundrel Rogue

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Rogue$Scoundrel
cat(currentClass$stats.htm)
```
####Class Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$features.htm)
```
<br/>

####Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$powers.htm)
```


##Wizard{.newPage}
###Build: Wizard Abjurer

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Wizard$Evoker
cat(currentClass$stats.htm)
```
####Class Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$features.htm)
```
<br/>

####Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
cat(currentClass$powers.htm)
```

