---
title: "Chapter B2 - Classes"
output: 
  html_document:
    highlight: null
    mathjax: null
    css: SFRPG.css

---



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
basedir <- dirname(getwd())
source(file.path(basedir,"scripts","1-01-Class-csv-to-html.R"))
classList <- getClassList(basedir)

printClassFeatures <- function (class)
{
  cat(class$stats.htm)
  cat('<h4>Class Features</h4>')
  cat(class$features.htm)
}

printClassPowers <- function (class)
{
    cat(class$powers.htm)
}

```



## Universal Powers
The following powers are available to Player Characters of all classes.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass  <- classList$Universal$Universal
cat(currentClass$powers.htm)
```

## Barbarian{.newPage}
### Barbarian Rager
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Barbarian$Rager
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Fighter{.newPage}
### Fighter Guardian
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Fighter$Guardian
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Priest{.newPage}
### Priest of Light
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Priest$Light
printClassFeatures(currentClass)
```

#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Rogue{.newPage}
### Rogue Scoundrel
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Rogue$Scoundrel
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Warlock{.newPage}
### Shadow Warlock
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Warlock$Shadow
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Warlord{.newPage}
### Warlord Tactician
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Warlord$Tactician
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```

## Wizard{.newPage}
### Wizard Elementalist
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
currentClass <- classList$Wizard$Elementalist
printClassFeatures(currentClass)
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
printClassPowers(currentClass)
```
