# Character Building

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_tables_equip <- get_equip_tables()


```

This chapter provides the rules for creating and levelling Player Characters. The overall character creation process is first described, and then each creation and levelling step is discussed in detail: stat generation, race and class selection, mundane equipment, feat selection, levelling up, and using magic items.


1. Overview
1. Stat Generation
1. Races
1. Classes
    - Paragon Paths
    - Epic Destinies
1. Equipment
1. Feats
1. Levelling
1. Magic Items


## Character Creation Overview

From the initial character concept to the point where the character sheet is complete, there are several decisions that a player must take in order to create a first level character. In this section, we explain the character creation process as a whole, and a more detailed discussion of each step is provided later on.

The basic steps for creating a character are:

1. Character concept and story
1. Race and Class selection
1. Ability generation
1. Skill selection
1. Equipment selection
1. Feat selection
1. Power selection
1. (Levelling)

<div class="tip">**Tip**: Although beginning players are encouraged to follow the character creation steps in order as listed above, it is quite possible to go back and forth between steps, as each decision provides new inspiration and ideas to improve on previous choices. Furthermore, since the number of available options may get overwhelming for inexperienced (and not so inexperienced) players, we provide pre-built sample characters that can be played as-is, or used as basic templates to be customized to taste. These sample characters, along with suggested level-up options up to level 30, can be found in the Classes chapter.</div>

## Character concept and story

...

## Race

...

## Class selection

### Power Source

### Role

### Class Build

### Class Powers


...


## Ability generation

Once the player has decided on a character class and a class build, the abilities for the Player Character can be generated. To do this, the player first selects Primary, Secondary, and Weak Abilities, and then assigns scores to each Ability by picking one of two possible Ability Arrays.

By selecting Primary, Secondary, and Weak Abilities, a player chooses what will be the strong and weak points of the Player Character. These choices are usually conditioned, if not fully determined, by the character's class and class build:

- The **Primary Ability** is the character's strongest and most important Ability, used for most attacks. Most class builds have a fixed Primary Ability.
- The **Secondary Ability** adds useful bonuses to several character Powers and Class Features. Many class builds have a predetermined Secondary Ability, though some provide a choice between two or three options.
- The **Weak Ability** is an Ability that sees little to no use for the character, and has the lowest score. Class builds should provide suggestions for suitable Weak Abilities, but the choice is otherwise up to the player.

The remaining three Abilities are considered **Tertiary Abilities**.

The next step is to assign scores to each Ability. To this end, there are two **Ability Arrays** that can be chosen: a **Focused Array** that concentrates on maximizing the Primary Ability (and hence the character's offensive potential), and a **Flexible Array** that provides a more balanced approach (resulting in a better Secondary Ability and higher average Secondary Defenses, Secondary Stats and Skills). The arrays assign the following scores to each Ability:

- Focused Array
    - +5 to Primary Ability
    - +2 to Secondary Ability
    - +0 to Tertiary Abilities
    - -1 to Weak Ability
- Flexible Array
    - +4 to Primary Ability
    - +3 to Secondary Ability
    - +1 to Tertiary Abilities
    - +0 to Weak Ability

<div class="tip">**Tip**: When deciding over an Ability Array, the Focused Array is a safe default option, whereas the Flexible Array can shine for characters whose Class Features and Powers strongly reward high Secondary Abilities.</div>

As a final step in the generation of Abilities, the player has to check the Favoured Abilities for the character's Race. Each Race typically has two or more Favoured Abilities, and characters whose Favoured Abilities match their Primary or Secondary Abilities gain Skill-related bonus:

- If either the Primary Ability or the Secondary Ability match a Favoured Ability, the character gains Skill Training as a bonus Feat.
- If both the Primary Ability and the Secondary Ability match Favoured Abilities, the character gains Skill Training and Skill Focus as bonus Feats.

See the Feat section later in this chapter for a description of these bonus Feats. The player can choose any legally available Skill for these Feats, and should do so after choosing class and racial Skills for the character (as described in the Skills section in this chapter).

<div class="tip">**Tip**: It is a good idea to take into account how racial Favoured Abilities match with the Primary and Secondary Abilities of each class build, when picking your Race and Class. However, if you really like a particular Race and Class combination with mismatched Abilities, you should not hesitate to take it - the Skill bonuses are a nice thing to have, but they won't make or break a character.</div>


<div class="compatibility">**Compatibility Note**: The Favoured Ability rule replaces racial Ability bonuses from older rulebooks. When a race provides a bonus to one or more Abilities, consider instead that these Abilities are Favoured Abilities.</div>


<div class="tip">**Tip**: Character Abilities remain constant across all levels, with a few exceptions. It is possible to increase Tertiary and Weak Abilities by taking certain high level Feats. As for Primary and Secondary Abilities, the only way to increase them is by taking specific Epic Destinies.</div>


<div class="compatibility">**Compatibility Note**: Under previous rules for levelling characters, Abilities increased naturally upon reaching certain levels. Ignore any mention to such Ability increases. In addition, whenever an Epic Destiny from an older rulebook provides a bonus to an Ability score, that bonus is halved (typically from +2 to +1).</div>

## Skill selection

Depending on their class, Player Characters can choose a number of Skills to become Trained in them. Characters gain a +3 bonus to Skill Checks with Trained Skills, and Skill Checks of Hard Difficulty are only available to characters with training in that Skill.

In order to select a Player Character's Skills, the player should look look at the Class Skill List for the character's class, as well as the Racial Skill List for the character's race. Any Skill in either of these lists can be selected as a Trained Skill for the character. The player then looks at the number of Trained Skills allowed by the character's class, and selects that many Trained Skills. 

<div class="compatibility">**Compatibility Note**: The Racial Skill rule replaces racial Skill bonuses from older rulebooks. When a race provides a numeric bonus to one or more Skills, consider instead that these Skills are Racial Skills. Any other Skill-related benefit, such as gaining Training with a specific Skill, remains unchanged. </div>

Some Races and Classes provide automatic training with predetermined Skills. In that case, the character first gains training with these skills, and then the player selects Trained Skills as usual.

A character whose Primary or Secondary Abilities match their racial Favored Abilities gains bonus Skill-related Feats. The Skills associated with these Feats are chosen after the selection of Trained Skills.

<div class="tip">**Tip**: When selecting Trained Skills, it is usually a good idea to prioritize Skills that match the character's Primary or Secondary Abilities. If you end up with training in two or more Skills associated with your Tertiary or Weak Abilities, consider taking Unnatural Ability as a Lesser Feat when you level up, in order to compensate for the lower Ability scores in these Skills.</div>

<div class="tip">**Tip**: As your character levels up, you can expand your Trained Skill selection by taking Skill Training as a Lesser Feat. Alternatively, you can specialize on your best Skills by taking Skill Focus as a Lesser Feat.</div>

For a detailed description of Skills and how to use them in the game, see the Skills section in the Adventuring chapter.


## Equipment selection

A character's class determines which weapons, implements and armor the character is proficient with. Upon creation, every character starts the game with the following items:
Up to three weapons the character is proficient with.
An armor the character is proficient with.
Up to one implement the character is proficient with.

In addition, starting characters get mundane equipment that has no impact on their stats and powers, including clothing, adventuring supplies, food, and money. The specific details should vary based on the character's background and the context of the initial adventure, and be the result of a dialogue between player and Game Master. We suggest, by default, providing characters with food for a week of travel, money to cover living for a month, and a non-exhaustive list of items to carry with them, such as bedrolls, rope, and torches. In addition, whenever a more unusual item of reasonable weight and cost is needed, we recommend the Game Master to assume that a character is carrying it, provided that the player can come up with a convincing explanation.

<div class="design">**Designer Note**: Some games aim to provide a detailed simulation of economy in a fantasy world. This is not such a game. We believe that keeping track of the specific contents of a player's backpack or the balance of each economic transaction are not critical to the game experience. Instead, we recommend players and Game Masters to keep inventories vague and flexible, outside of player rewards like Magic Items, or items of special importance to the game plot.

That said, if you favor more detailed rules for economy, there are tables with recommended item costs and weights from other game systems, such as D20SRD  (http://www.d20srd.org/indexes/equipment.htm )and 13AGESRD (http://www.13thagesrd.com/equipment ), which are freely available online. You can use these tables as a reference for setting item prices in your campaign.</div>

In the rest of this section, we list the weapons, armor and implement available in the game, along with a description of their rules.

### Weapons

Each weapon in the game is described by the following elements:

- **Name**
- **Family**: A category of weapons with similar properties. For example, Axes is a weapon family that includes hand axes, battle axes, and greataxes. 
- **Damage**: Base damage dealt per weapon damage die.
- **Keywords**: Special properties associated with the weapon.
- **Training**: How much training is required to wield the weapon, determines which classes can use it.
- **Type**: Whether it is a Melee or Ranged weapon.
- **Hands**:Whether the weapon requires 1 or 2 hands to be wielded.

A character's class determines which weapons the character is trained to use. A character using a weapon without training does not benefit from any of the weapon's properties, including damage, keywords, and any magic abilities. Instead, the weapon is treated as an Light Improvised Weapon if it requires one hand to wield, or a Heavy Improvised Weapon if it requires two hands. Improvised weapons can be used without training.

<div class="compatibility">**Compatibility Note**: In older rulebooks, weapon training is referred to as weapon proficiency, and weapons can have a Proficiency Bonus to hit, if the character is trained with them. This Proficiency Bonus no longer exists, and any mentions to it should be ignored. </div>

<!-- 
Weapons
Proficiency
Using without proficiency: improvised weapons
Discussion: Main Hand, Off-hand
Weapon types and categories
Weapon keywords
-->

#### Weapon Families

The following weapon families are supported in the game:

- **Axe**: Melee weapon consisting of a heavy edged head and a handle.
- **Bow**: Ranged weapon consisting of a strip of wood or other flexible material and a string, used to shoot arrows.
- **Crossbow**: Ranged weapon consisting on a bow mounted on a stick and a mechanism to hold the string. Used to shoot bolts.
- **Flail**: Melee weapon consisting on a blunt or spiked head attached to a handle by a chain or rope.
- **Hammer**: Melee weapon consisting of a heavy blunt head and a handle.
- **Heavy Blade**: Melee weapon with a long and heavy blade 
- **Improvised**: A common object used as a weapon, or a weapon used without training. 
- **Light Blade**: Melee weapon with a short or slender blade
- **Sling**: Ranged weapon consisting of a pouch and a string, used to throw stones or bullets.
- **Spear**: Melee weapon consisting of a pointed head attached to a long shaft.
- **Staff**: Melee weapon consisting of a long wooden shaft.
- **Unarmed**: A character's own body used as a melee weapon.

<div class="tip">**Tip**: Weapon Family is of special relevance in relation to the Weapon Focus category of Feats, as these Feats often give bonuses when wielding any weapon of a specific family. Advanced players are encouraged to study the different Feat bonuses when considering their weapon of choice. For beginning players, we suggest instead to choose based on aesthetic preferences - you can always use the Retraining rule to rethink your choice at a later point.</div>

#### Weapon Keywords

The following weapon keywords are supported in the game:

- **Off-Hand**: The weapon can be wielded in the off-hand while another weapon or object is wielded in the main hand. When a character is simultaneously wielding two Off-Hand weapons, these weapons gain the Parry keyword (+1 AC vs melee).
- **Parry**: A character wielding one or more weapons with Parry gains +1 to AC against melee attacks. The bonus from multiple weapons with this keyword does not stack.
- **Range**: Ranged weapons have the Range keyword, followed by two numbers. The first number is the Short Range, the maximum distance at which the weapon can make Ranged and Area attacks without penalty. The second number is the Long Range, the maximum distance at which the weapon can make Ranged and Area attacks with a Long Range penalty (-2 hit).
- **Reach**: Weapons with reach increase the Melee Reach for attacks made with them by a certain amount. A medium-sized character typically has a Melee Reach of 1, which increases to 2 with a Reach +1 weapon, and to 3 with a Reach +2 weapon.
- **Recharge**: -2 to hit unless the wielder has spent a move action to recharge this weapon since last drawing it or attacking with it.
-- Recharge (move action). Move 1 square. You can ignore the Recharge penalty to hit with one of your weapons for your next attack power with that weapon.
- **Throw**: Melee weapons with Throw can be used to make Ranged and Area attacks as well as Melee and Close attacks. The Throw keyword is followed by two numbers. The first number is the Short Range, the maximum distance at which the weapon can make Ranged and Area attacks without penalty. The second number is the Long Range, the maximum distance at which the weapon can make Ranged and Area attacks with a Long Range penalty (-2 hit). After using a Ranged or Area attack power with a Throw weapon, choose a character targeted by the attack. The weapon is placed on the ground in a square in the character's space. Magical Weapons with Throw are automatically returned to the wielder's hand after each attack instead.
- **Unwieldy**: Attacks made with this weapon gain a -1 penalty to hit.
- **Versatile**: When wielded on the main hand with a free off-hand, this weapon deals +1 damage per weapon damage die. This increases to +2 damage per weapon damage die at level 16.
- **Very Unwieldy**: Attacks made with this weapon gain a -2 penalty to hit.

<div class="compatibility">**Compatibility Note** In older rulebooks, Throw weapons can be classified as Heavy Thrown or Light Thrown. Treat any mention to either of these as referring to Throw weapons instead.</div>

#### Weapon Hands

The hand requirements to use a weapon are as follows:

- **One-handed weapons without the Off-Hand keyword** can be wielded in the character's **main hand**. The character can wield another item, such as an Off-Hand weapon, an implement or a Shield, in the Off-Hand.
- **One-handed weapons with the Off-Hand keyword** can be wielded in the character's **main hand or off-hand**. The character can wield another item, such as an Off-Hand weapon, an implement or a Shield, in the other hand. When a character wields an Off-Hand weapon in each hand, these weapons gain the Parry keyword (+1 AC vs melee).
- **One-handed weapons with the Versatile keyword** can be wielded in **one hand** like regular one-handed weapons. However, if the **other hand is free**, the character gains a **damage bonus** when using the weapon of +1 per weapon damage die (which increases to +2 at level 16). Versatile weapons wielded while leaving a hand free count as two-handed weapons for any Power or Class Feature that references two-handed weapons.
- **Two-handed weapons** require both hands to be wielded. A character cannot use a hand to wield any other item while wielding such a weapon.

<div class="tip">**Tip**: It is usually better to use two-handed weapons, or Versatile weapons with a free hand, if you want your character to focus on the offense, and a one-handed weapon with a shield or two Off-Hand weapons, if you prefer focusing on defense. Wielding a weapon in each hand does not grant additional attacks or any other inherent benefits (aside from the Parry keyword granted when dual wielding Off-Hand weapons), so it is usually not a good idea, unless you have class Powers or Features that require dual wielding or otherwise reward you for it.</div>

#### Weapon Tables

The tables below provide stats for all weapons in the game, classified by the type of training they require, whether they are melee or ranged weapons, and the number of hands they require.


##### Basic Weapons
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
sfrpg::extract_equip_table(df_tables_equip, 'Weapons', 'Basic') %>% cat()
```

##### Improvised Weapons
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
extract_equip_table(df_tables_equip, 'Weapons', 'Improvised') %>% cat()
```
##### Martial Weapons
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
extract_equip_table(df_tables_equip, 'Weapons', 'Martial') %>% cat()
```
##### Inner Weapons
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
extract_equip_table(df_tables_equip, 'Weapons', 'Inner') %>% cat()
```


Some character classes use unique weapons not available to other classes. In these cases, stats for these weapons should be provided within the class rules.

<div class="compatibility">**Compatibility Note**: Some weapon types from older rulebooks are no longer supported. As a general rule, we recommend treating any such weapon as a currently supported weapon of the same Family, Training, Type, and Hand requirements, if available. Some cases of particular interest are:
Two previously existing weapon families, Picks and Maces, have been discontinued. We recommend replacing Picks with Axes of similar properties, and replacing Maces with Hammers of similar properties. 

Some weapons used to have the same name as their weapon family. To remove this ambiguity, they have been renamed:

- **Spear** is now Halfspear
- **Crossbow** is now Light Crossbow
- **Flail** is now Light Flail

Some character classes from older sourcebooks have bonuses associated with obsoleted weapon types. We recommend the following replacements for these weapons:

- **Sickle**: replace with Dagger
- **Scimitar**: replace with Short Sword
- **Club**: replace with Mace</div>

### Armor

Each armor in the game is described by the following elements:

- **Name**
- **AC bonus**: Bonus granted to a character's AC for wearing the armor with training.
- **Type**: Whether the armor is Light Armor or Heavy Armor, or a Shield. 
- **Armor Penalty**: Penalty granted to Initiative and many Skills for wearing the armor.
- **Movement Penalty**: Penalty granted to a character's Speed (for all available movement types) for wearing the armor.

Each character can wear one suit of Light Armor or Heavy Armor. In addition, each character can use one Shield. Characters wearing nothing but plainclothes, or wearing no clothes, are considered as wearing Cloth Armor. Using a shield takes up one hand, and characters cannot wield weapons or implements nor carry objects with their shield hand.

A character's class determines which armors the character is trained to use. A character using an armor without training does not benefit from any of the armor's properties, including AC bonus and any magic abilities. However, any Armor Penalty or Movement Penalty imposed by the armor still applies. All characters are considered to be trained in the use of Cloth Armor.

A character using a Shield and wearing Light Armor or Heavy Armor can add the AC bonuses from shield and armor. However, Armor Penalties and Movement Penalties are also added.

Some character classes gain an additional bonus to AC while wearing Light Armor. This is called Light Armor AC Bonus. Some classes also have class features that grant a bonus to AC, and these can stack with their Light Armor AC Bonus. A table summarizing Light Armor AC Bonus and other stats for all classes currently in the game (including classes from older rulebooks) is provided in this chapter, in the Race and Class Selection section. 

To summarize, a character's AC is calculated as follows:
```
AC= 10 + Armor bonus + Shield bonus + Class Light Armor bonus
```

Note that these are the most common types of AC bonus, but other bonuses granted by specific Class Features, Feats, or Powers can still apply.

<div class="compatibility">**Compatibility Note**: Unlike other defenses, a character's Abilities provide no bonus to that character's AC. In older rulebooks this was not the case, and it was common to have character classes whose Class Features allowed using an Ability as a bonus to AC while wearing Light Armor. Ignore these bonuses, and any other mention of an Ability bonus to AC. Fixed bonuses to AC that do not depend on a character's Abilities still apply as normal.</div>

#### Armor Types

The different types of armor available in the game are described as follows:

- Light Armor
    * **Cloth**: Regular clothing, or Robes
    * **Leather**: A combination of regular clothing and leather pieces for added protection, such as a leather jacket or coat, a leather suit, or leather breastplates.

- Heavy Armor
    * **Hide**: A combination of regular clothing, leather pieces, and thick pieces of beast skin for added protection.
    * **Chain**: Armor made of interlocking metal rings.
    * **Scale**: Armor made of small, overlapping metal scales.
    * **Plate**: Armor made of large metal plates.

- Shield
    * **Light Shield**: Shield of reduced size and weight.
    * **Heavy Shield**: Large shield that covers most of a character's body.
    
#### Armor Table

The table below provides stats for all types of armor in the game:

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
extract_equip_table(df_tables_equip, 'Armor') %>% cat
```


### Implements

Each implement in the game is described by the following elements:

- **Name**
- **Hands**: Whether the implement requires a hand, two hands, or no hands at all to wield.
- **Keywords**: Special properties associated with the implement.
- **Range**: base range for Implement Ranged Basic Attacks made with the implement.

Note that, unlike weapons, implements do not have an associated damage die. Damage in implement attacks is not affected by the choice of implement. The only mechanical differences between implements are their hand requirements, the bonuses provided by their associated Implement Focus Feats, and the range for Implement Ranged Basic Attacks (but not for other ranged attacks). The rules for Implement Ranged Basic Attacks are in the Stat Generation section of this chapter.

A character's class determines which implements the character is trained to use. A character wielding no implement, or wielding an implement without training uses the "No Implement" stats, which include a -2 penalty to hit due to the Very Unwieldy property. A character using an implement without training does not benefit from any of the implement's properties, including damage, keywords, and any magic abilities. 

#### Implement Types

The following implement types are supported in the game:

- **Staff** - Long shaft, usually made of wood.
- **Wand** - Short, slender stick.
- **Rod** - Long, decorated stick.
- **Orb** - Sphere made of a transparent or reflective material
- **Tome** - Heavy leather-bound book with inscribed spells
- **Symbol** - Amulet or necklace bearing the symbol of a deity
- **Focus** - Small carried object used to channel inner energy
- **Totem** - Carved figure representing an animal, plant, or spirit.
- **Weapon Implement** - Weapon that can be used to channel supernatural powers. Some character classes allow specific types of weapons to be used as Weapon Implements. Weapon Implements require the same number of hands to wield as their associated weapons.
- **No Implement** - A character using just hand gestures to channel power.

#### Implement Keyword

The following implement keywords are supported in the game:

- **Very Unwieldy**: Attacks made with this implement gain a -2 penalty to hit.

#### Implement Hands

The hand requirements to use a weapon are as follows:

- **No Hand implements** do not require any free hands to be wielded.
- **One-handed implements** can be wielded in the character's **main hand** or **off-hand**.
- **Two-handed implements** require both hands to be wielded. A character cannot use a hand to wield any other item while wielding such an implement.

#### Implement Table

The table below provide stats for all implements in the game:

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
extract_equip_table(df_tables_equip, 'Implements') %>% cat
```


## Feats
<!-- 
definition of feat

feat elements
category
keywords
unlimited
repeatable
level
requirements
effect

picking a feat
requirements
see retraining, on levelling

starting character: level 1 feats
toughness
focus
armor focus
proficiency

higher level feats

level 4 feats
role 1
role 2
multiclass

level 11 feats
power source
role 3
paragon ability

level 21 feats
epic versatility
epic might
epic ability
-->

A Feat is a character customization option that lets player specialize their characters beyond their Race, Class, and Power selection. Each Feat provides a significant improvement to the character's combat capabilities. Characters start the game with one Feat, and gain additional ones as they level up, to a maximum of nine. On top of that, characters may gain bonus feats from other sources, such as their Race or Class. Depending on the specific case, a character gaining a bonus Feat may be able of picking any available Feat of a certain level or lower, or of picking any feat within a given Feat Category, or just gain a predetermined Feat.

Each Feat is composed of the following elements:

- **Name**
- **Level**: The minimum level at which the Feat can be acquired. Also, the minimum level of the Feat Slot that can be used to learn the Feat.
- **Category**: A group of Feats that perform a similar function. A character can only select a single Feat from each Feat Category.
Some Feat Categories are labeled as “Unlimited”. A character can select any number of Feats from an Unlimited Category
- **Keywords**: A series of labels that describe the Feat. Feat Keywords are purely descriptive and have no associated rules, but are sometimes referenced by other Feats.
- **Requirements**: A series of conditions that a character must meet before taking the Feat.
- **Description**: The benefits granted by the feat.
- **Summary**: An abbreviated version of the Feat Description, used in summary tables. The Summary text does not necessarily provide exact or complete rules, and should only be used as a quick guide for character building decisions, not as a rules reference.

In addition to regular Feats, characters can also gain Lesser Feats, which are customization options that usually improve a character's adventuring capabilities but have little or no impact in their combat performance. Through Lesser Feats, characters can expand their knowledge in Skills, Rituals, or languages. Characters start the game with no Lesser Feats but acquire them as they level up, to a maximum of nine. On top of that, characters may gain bonus Lesser Feats from other sources, such as their Race or Class, or other Feats. Depending on the specific case, a character gaining a bonus Lesser Feat may be able of picking any available Lesser Feat of a certain level or lower, or just gain a predetermined Lesser Feat.

Each Lesser Feat is composed of the following elements:

- **Name**
- **Level**: The minimum level at which the Lesser Feat can be acquired. Also, the minimum level of the Lesser Feat Slot that can be used to learn the Lesser Feat.
- **Repeatable**: Whether the Lesser Feat can be taken multiple times.
- **Keywords**: A series of labels that describe the Feat. Feat Keywords are purely descriptive and have no associated rules, but are sometimes referenced by other Feats.
- **Requirements**: A series of conditions that a character must meet before taking the Lesser Feat .
- **Description**: The benefits granted by the Lesser Feat .
- **Summary**: An abbreviated version of the Lesser Feat Description, used in summary tables. The Summary text does not necessarily provide exact or complete rules, and should only be used as a quick guide for character building decisions, not as a rules reference.

The following table summarizes the acquisition of  Feat Slots and Lesser Feat Slots per character level:

Level | Slots aquired | Total Feats  | Total Less. Feats  | Feat levels | Lesser Feat levels
------------- | -------------|--|-- |--|--
 1| Gain a Level 1 Feat Slot | 1 | 0 | 1 | 
 2| Gain a Level 2 Lesser Feat Slot | 1 | 1| 1 | 2
 4| Gain a Level 4 Feat Slot | 2 | 1| 1,4 | 2
 6| Gain a Level 6 Lesser Feat Slot | 2 | 2| 1,4 | 2,6
 8| Gain a Level 8 Feat Slot | 3 | 2| 1,4,8 | 2,6
 10| Gain a Level 10 Lesser Feat Slot | 3 | 3| 1,4,8 | 2,6,10
 11| Gain a Level 11 Feat  Slot | 4 | 3|1,4,8,11  | 2,6,10
 12| Gain a Level 12 Lesser Feat Slot | 4 | 4| 1,4,8,11 | 2,6,10,12
 14| Gain a Level 14 Feat Slot | 5 | 4| 1,4,8,11,14  | 2,6,10,12
 16| Gain a Level 16 Lesser Feat Slot | 5 | 5| 1,4,8,11,14 | 2,6,10,12,16
 18| Gain a Level 18 Feat Slot | 6 | 5| 1,4,8,11,14, 18  | 2,6,10,12,16
 20| Gain a Level 20 Lesser Feat Slot | 6 | 6| 1,4,8,11,14, 18  | 2,6,10,12,16, 20
 21| Gain a Level 21 Feat Slot | 7 | 6| 1,4,8,11,14, 18,21  | 2,6,10,12,16, 20
 22| Gain a Level 22 Lesser Feat Slot | 7 | 7| 1,4,8,11,14, 18,21  | 2,6,10,12,16, 20,22
 24| Gain a Level 24 Feat  Slot | 8 | 7| 1,4,8,11,14, 18,21,24  | 2,6,10,12,16, 20,22
 26| Gain a Level 26 Lesser Feat Slot | 8 | 8| 1,4,8,11,14, 18,21,24  | 2,6,10,12,16, 20,22,26
 28| Gain a Level 28 Feat Slot | 9 | 8| 1,4,8,11,14, 18,21,24,28  | 2,6,10,12,16, 20,22,26
 30| Gain a Level 30 Lesser Feat Slot | 9 | 9| 1,4,8,11,14, 18,21,24,28  | 2,6,10,12,16, 20,22,26,30



Each Feat Slot can be used to gain a Feat with a level equal or lower to that of the Feat Slot. Likewise, each Lesser Feat Slot can be used to gain a Lesser Feat with a level equal or lower to that of the Lesser Feat Slot. Note that Feats and Lesser Feats are not interchangeable: a Feat Slot cannot be used to gain Lesser Feats, nor can a Lesser Feat slot be used to gain Feats.

<div class="tip">**Tip**: Although the power level of Feats tends to grow with their level, the differences are sometimes very small. Often, a lower level Feat will be just as effective for a given character as the higher level alternatives, if not the best option altogether.</div>


<div class="tip">**Tip**: At some levels, a Feat Slot can only be filled with lower level Feats.</div>


<div class="tip">**Tip**: If you are lost, or want to experiment, choosing legal Feats at random is still expected to yield competent (if unfocused) characters.</div>


<div class="compatibility">**Compatibility Note**: Feats from older rulebooks are considered obsolete and should not be used. This is not, strictly speaking, due to compatibility issues (since the Feats should mostly work under the current rules), but as a way to improve the game experience - see the Designer's Note below for a detailed explanation. That said, Game Masters who wish to incorporate older Feats into their campaigns can do so with minimal translation effort, as long as they are aware that they risk breaking design assumptions about combat length and difficulty, and class balance.</div>


<div class="design">**Designer Note**: Experienced players may find this Feat system too restrictive compared to those of previous games. However, these restrictions serve an important purpose. Here is the reasoning behind them:

- **Separation between combat options and adventuring options**: Allowing characters to freely choose between combat and non-combat Feats results in excessive performance variability, to the point that it's virtually impossible to design high level content that will be moderately difficult and enjoyable to both characters that are completely specialized on combat and characters that only select non-combat Feats. Furthermore, it is usually optimal to ignore either combat or non-combat options (depending on the campaign), resulting in roughly half the Feats in the game seeing little to no play. By splitting customization slots between combat options (Feats) and non-combat options (Lesser Feats), we get much more predictable character outcomes, which allow for a better high level game experience. This also allows players to improve both their combat and non-combat capabilities without feeling that they are hurting their character's potential.
- **Feat categories**: It is a natural thing for players to experiment with spending all of their customization resources in improving a single dimension of their character, such as damage, or defenses, or even mobility. Again, this leads to excessive variability between high level character builds and, as a consequence, high variability in game difficulty, combat length, and overall game experience. By classifying Feats into functional Categories, and restricting players to one Feat per Category, we can, for example, provide dozens of options to increase attack damage while ensuring that a given character will only be able to have two or three of them at once.
- **No support for previous Feats**: We wanted every Feat in the game to have a purpose, and to be playable for a significant percentage of character builds. However, older rulebooks had thousands of Feats with wildly inconsistent quality and power level. We decided that starting from scratch and having a compact set of Feats that could realistically be tested and polished was the best option.
- **No class/race requirements**: We wanted the total number of feats to be manageable for players, but also to maintain backwards compatibility with previous Races and Classes. Since older rulebooks have dozens of Races and Classes, and including Feats for only a subset of them would be considered unfair and introduce balance issues, we chose to remove racial feats altogether and replace Class Feats with options based on Class Role and Power Source, which fill a similar niche with much less effort and complexity. That said, we might reconsider this for future supplements.</div>


TODO: REWORD RACIAL ABILITIES TO DECOUPLE THEM FROM LESSER FEATS. JUST GRANT SKILLS.



## Power selection
## Stat generation
Fill in the blanks
IMPLEMENT RANGED BASIC ATTACK IS GENERATED HERE
## Levelling 
## Magic Items
