# Classes


```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_class = get_l_class()

print(get_l_class)

```


## Universal Powers
The following powers are available to Player Characters of all classes.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Universal', 'Universal') 
df_class_build$htm_power %>% cat
```

## Barbarian{.newPage}
### Barbarian Rager
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Barbarian', 'Rager')
df_class_build$htm_stat %>% cat
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Fighter{.newPage}
### Fighter Guardian
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Fighter', 'Guardian')
df_class_build$htm_stat %>% cat

df_class_build$htm_feature
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Priest{.newPage}
### Priest of Light
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Priest', 'Light')
df_class_build$htm_stat %>% cat
df_class_build$htm_feature %>% cat
```

#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Rogue{.newPage}
### Rogue Scoundrel
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Rogue', 'Scoundrel')
df_class_build$htm_stat   %>% cat
df_class_build$htm_feature %>% cat
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Warlock{.newPage}
### Shadow Warlock
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Warlock', 'Shadow')
df_class_build$htm_stat   %>% cat
df_class_build$htm_feature %>% cat
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Warlord{.newPage}
### Warlord Tactician
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Warlord', 'Tactician')
df_class_build$htm_stat %>% cat
df_class_build$htm_feature %>% cat
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```

## Wizard{.newPage}
### Wizard Elementalist
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_class, 'Wizard', 'Elementalist')
df_class_build$htm_stat   %>% cat
df_class_build$htm_feature %>% cat
```
#### Class Powers{.newPage}
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat
```
