# Magic Items


## Magic Weapons

Magic Weapons grant a bonus to damage:

- Heroic: +1 damage
- Paragon : +3 damage
- Epic: +6 damage

<br/><br/>

```{r magic_weapon, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Weapon')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Magic Implements

Magic Implements grant a bonus to damage:

- Heroic: +1 damage
- Paragon : +3 damage
- Epic: +6 damage

<br/><br/>

```{r magic_impl, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Implement')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Magic Armor

Magic Armor grants a bonus to damage:

- Heroic: +4 HP
- Paragon : +12 HP
- Epic: +24 HP

<br/><br/>

```{r magic_armor, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Armor')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Neck Items
```{r magic_neck, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Neck')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Feet Items
```{r magic_feet, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Feet')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Waist Items
```{r magic_waist, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Waist')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Head Items
```{r magic_head, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Head')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Arms Items
```{r magic_arms, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Arms')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Hands Items
```{r magic_hands, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Hands')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Magic Rings
```{r magic_ring, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Ring')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Wondrous Items
```{r magic_wondrous, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Wondrous Item')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```

## Consumable Items
```{r magic_consumable, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_items_raw <- read_my_csv('magic_items') %>% dplyr::filter(type=='Consumable')
htm_items = clean_df_items(df_items_raw)
htm_items %>% cat()
```