# Monsters

To generate a standard monster, pick a monster race and a monster class.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
```

Note - Recharging attacks:
- Some monsters have attacks with (recharge n+). These attacks are spent on use, and cannot be used again
  until recharged.
- At the end of a monster's turn, roll 1d6 for each spent recharge attack that wasn't used this turn. If
  the roll is equal or higher to the recharge value, the attack is recharged.
- PCs are aware when a monster they can see succeeds at recharging. They don't know details about
  the recharged power, but they can find out with a Skill Check (see Skills chapter).
- Some recharge attacks are labeled as Exhausted: monsters start combat with these powers spent.

## Standard Monsters


### Monster Races - Heroic, Humanoid
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Humanoid')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Races - Heroic, Undead
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Undead')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Races - Heroic, Beast
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Beast')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Races - Heroic, Other

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard', subcategory %in% c('Aberration', 'Plant', 'Ooze'))
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Classes - Mundane

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Mundane')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

### Monster Classes - Humanoid

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Humanoid')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

### Monster Classes - Elemental

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Elemental')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```


## Minion Monsters

Unlike most characters, minions do not have a HP value - do not keep track of damage done to minions. Instead, use
the following:

- Minions have a damage threshold value. Whenever a minion receives damage equal or greater than their damage threshold,
  they are automatically incapacitated. If a character damages a minion multiple times in the same turn (e.g. with
  several weak attacks) and the total damage that turn exceeds the minion’s damage threshold, the minion is also
  automatically incapacitated.
- A minion that takes damage below their damage threshold is knocked prone instead.
- Prone minions that are targeted by an attack or take any damage are automatically incapacitated. A minion that starts
  their turn Prone must make a saving throw - on a failed save, they can take no actions that turn.

In addition, most minions have Partial Vulnerability (Melee or Ranged), included in their stats.

### Minion Races, Heroic Humanoid

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Humanoid')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Races, Heroic Undead

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Undead')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Races, Heroic Beast

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Beast')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Races, Heroic Other

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory %in% c('Plant', 'Ooze'))
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Classes

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Minion', subcategory=='Mundane')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

## Elite Monsters

All Elite Monsters gain the following rules:

- Action Point: Each Elite Monster has 1 Action Point, which can be spent with an
  Action Point Check, using the same rules as PCs.
- Endure Conditions: At the start of their turn, an Elite Monster can choose a Combat
  Condition afflicting them, and make a Saving Throw. On a successful save, the condition
  is downgraded until their next turn, and they take 2(E) damage.


### Elite Monster Templates:

Apply to Standard monsters to convert them to Elite

Basic Elite Monster:
- Double XP value
- Double HP
- Trait: Elite Attack: Melee and Ranged attacks can target 1 additional enemy in range.
  Area and Close attacks have Burst size increased by 1. Damaging attacks that target a
  single enemy deal +D/2 damage.
  
### Elite Monster Races

Monsters with the following classes gain the Elite monster special
rules, double XP and double HP (already included in stats).

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Elite')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Elite Monster Classes

Monsters with the following classes gain the Elite monster special
rules, double XP and double HP.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Elite')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

## Solo Monsters

All Solo Monsters gain the following rules:

- Action Point: Each Solo Monster has 2 Action Points, which can be spent with an
  Action Point Check, using the same rules as PCs.
- Endure Conditions: Twice at the start of their turn, a Solo Monster can choose a Combat
  Condition afflicting them, and make a Saving Throw with a +5 bonus. On a successful save, the condition
  is downgraded until their next turn, and they take 2(E) damage.

### Solo Monster Races - Dragon

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(category=='Solo', subcategory=='Dragon')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Solo Monster Classes - Dragon


```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Solo')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

## Other Templates

Fat:
- +50% XP value
- Double HP

Veteran:
- +25% XP value
- +6/12/24 HP, depending on tier
- +2/4/8 D, depending on tier
- +1H, +1Def

## Base Stats

In this section, we show monster templates with basic stats that can be used
as reference when designing custom monsters.

### Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Race - Paragon
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()>=11, Level %>% as.numeric()<21, category=='Standard', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Race - Epic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()>=21, category=='Standard', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Class

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Example')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

### Minion Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Class

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Minion', subcategory=='Example')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

### Solo Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Solo', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Solo Race - Paragon
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()>=11, Level %>% as.numeric()<21, category=='Solo', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Solo Race - Epic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()>=21, category=='Solo', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```