# Monsters

To generate a standard monster, pick a monster race and a monster class.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
```

## Standard Monsters


### Monster Races - Heroic, Humanoid
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Humanoid')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Races - Heroic, Undead
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Undead')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Races - Heroic, Beast
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard',subcategory=='Beast')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Classes - Mundane

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Mundane')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

### Monster Classes - Elemental

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Elemental')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```

## Minion Monsters

Unlike most characters, minions do not have a HP value - do not keep track of damage done to minions. Instead, use
the following:

- Minions have a damage threshold value. Whenever a minion receives damage equal or greater than their damage threshold,
  they are automatically incapacitated. If a character damages a minion multiple times in the same turn (e.g. with
  several weak attacks) and the total damage that turn exceeds the minion’s damage threshold, the minion is also
  automatically incapacitated.
- A minion that takes damage below their damage threshold is knocked prone instead.
- Prone minions that are targeted by an attack or take any damage are automatically incapacitated. A minion that starts
  their turn Prone must make a saving throw - on a failed save, they can take no actions that turn.

In addition, most minions have Partial Vulnerability (Melee or Ranged), included in their stats.

### Minion Races, Heroic Humanoid

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Humanoid')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Races, Heroic Undead

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Undead')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Races, Heroic Beast

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Beast')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Classes

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Minion')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

## Base Stats

In this section, we show monster templates with basic stats that can be used
as reference when designing custom monsters.

### Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Class

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard', subcategory=='Example')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

### Minion Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion', subcategory=='Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>%
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Minion Class

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Minion', subcategory=='Example')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( )
htm_monster_class %>% cat()
```