# Monsters

To generate a standard monster, pick a monster race and a monster class.

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
```

## Standard Monsters


### Monster Races - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Classes

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

## Minion Monsters

### Monster Races - Heroic

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Minion')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Monster Classes

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Minion')
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```

## Base Stats

In this section, we show monster templates with basic stats that can be used
as reference when designing custom monsters.

### Base Stats - Race - Heroic
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_race <- read_csv_monster("monster_races") %>%
  dplyr::filter(Level %>% as.numeric()<11, category=='Standard - Example')
htm_monster_race <- get_htm_monster_race(df_monster_race)  %>% 
    get_monster_list_htm()
htm_monster_race %>% cat()
```

### Base Stats - Class

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_monster_class <- read_csv_monster("monster_classes") %>%
  dplyr::filter(category=='Standard - Example') 
htm_monster_class <- get_htm_monster_class(df_monster_class)  %>%
   get_monster_list_htm( ) 
htm_monster_class %>% cat()
```