# Optional Material

Character options in this section can be used with the GM's consent.

## Origins

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
library(sfrpg)
df_origin = get_df_origin()
```


### Shifter - Agile

Shifters have the ability to partially change their shape, gaining animal traits.
Agile Shifters often take the form of wolves, panthers or other beasts that favor
speed and cunning over brute force.

#### Origin Stats
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_origin, 'Shifter', 'Agile')
df_class_build$htm_stat %>% cat()
```


#### Origin Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_feature %>% cat()
```

#### Origin Powers
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat()
```


### Shifter - Brute

Shifters have the ability to partially change their shape, gaining animal traits.
Brute Shifters often take the form of bears, boars or other beasts that favor
brute force over speed and cunning.

#### Origin Stats
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build = get_class_build(df_origin, 'Shifter', 'Brute')
df_class_build$htm_stat %>% cat()
```


#### Origin Features
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_feature %>% cat()
```

#### Origin Powers
```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE}
df_class_build$htm_power %>% cat()
```