---
title: "Feats"
output: 
  html_document:
    css: "C:\\Users\\acer\\Documents\\Perico\\OCIO\\SFRPG-web\\raw\\SFRPG.css"
---



```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE,cache=FALSE}
library(plyr)
library(reshape2)
library(dplyr)

source('~/Perico/Trabajo/COM/Codigo/R/utils/plyr.nested.R')
source('~/Perico/OCIO/SFRPG-web/scripts/Feat-csv-to-html.R')


#cat(attr(getFeatSection(getFeatList()$feats),"full"))
featlist <- getFeatList()

```
###Level 1 Feats

Categories:

- Defense Focus
- Offense Focus
- Toughness

<div class="tip">**Tip**: Toughness is a good level 1 Feat for starting players who don’t want to complicate themselves.</div>

<div class="tip">**Tip**: Feats in the Toughness category are generally better than Defense Focus feats at providing raw survivability. Feats in the Defense Focus category are usually better at providing protection against melee attacks, or for characters that are interested in their secondary benefits. When in doubt, take both.</div>

<div class="tip">**Tip**: Offense Focus Feats are the one of the main reasons to choose one Weapon Family over another, or one type of Implement over another. The other reason is the player’s aesthetic preference - some people just like axes a lot. Players who carefully study all options to choose the one that best suits their character build will probably gain a small edge in combat, but the Feats are designed to be close in power level, so choosing based on personal taste will be almost as effective.</div>


```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE,cache=FALSE}
cat(attr(featlist$feats$"1"$"Defense Focus","section"))

cat(attr(featlist$feats$"1"$"Offense Focus","section"))

cat(attr(featlist$feats$"1"$"Toughness","section"))

```


###Level 1 Optional Feats

Can be used with GM’s consent

Categories:

- Armor Training
- Weapon Training


<div class="tip">**Tip**: Armor Training is usually not as strong as Defense Focus, but they both stack, and you can take multiple Training feats.</div>

<div class="tip">**Tip**: Weapon Training is usually worse than an Offense Focus up to level 15, and stronger after level 16. They both stack.</div>

<div class="tip">**Tip**: There is no Implement Training Feat. If you are really interested in using a different Implement, go Multiclass and take Multiclass Implement or, alternately, convince your GM that you want it for story reasons and not to optimize your character.</div>

<div class="tip">**GM Tip**: If your player is really interested in getting training with a different Implement, allow them to have it for free if they provide a convincing argument. When in doubt, make it conditional on them taking an Offense Focus Feat that is not specific to that implement, such as Dual Focus.</div>

<div class="design">**Designer Note**: These are not needed from a mechanical standpoint. In terms of game systems, they are redundant, or slightly imbalanced, or cost too much in terms of complexity to be worth it. However, it’s stuff that players often want and, at worst, it won’t break the game too badly. I recommend GMs to leave these off the table for beginning players, and allow them once the group is experienced enough to know what they are doing, or in case someone really wants a Greatsword-wielding wizard or a Fireball-casting rogue.</div>

```{r, echo=FALSE, results='asis', message=FALSE, warning=FALSE, prompt=FALSE,cache=TRUE}
cat(attr(featlist$feats$"1"$"Armor Training","section"))
cat(attr(featlist$feats$"1"$"Weapon Training","section"))


```





